\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Team 77 Video Project}
\author{Hector Sanchez and Samantha Felzien}
\date{April 2020}

\begin{document}

\maketitle


\begin{itemize}
    \item General Theme: The general theme of our final video will be based around showcasing our sourdough based program and/or will have a comical note to the presentation. The theme could also involve memes but will certainly involve a comedic taste.
    \item The ideas we want to get across will be why Scala is so different from other languages and what exactly these differences are. We will also show what are some of the challenges with Scala and where the disadvantages with this languages occur.
    \item The code samples we will show will most likely be our simple programs that do mildly useful things but also have some comedic value or are easy to explain. We will also focus on showcasing code that makes the Scala language unique or where it excels above other languages.
    \item For our demo program we will most likely screen record the entire process of going through our program and depending on time constraints we may also edit the footage to include some sort of graphic or image to compliment the baking process within our program
    \item As for footage, we will most likely use Zoom to coordinate our physical efforts, but if need be we could also just each focus on a certain half of the project and present it that way, later splicing the footage together to make one singular piece. We can also work to edit home footage into these videos for further demonstration purposes.
\end{itemize}

\end{document}

